A pipeline to analyse time-course gene expression data

### 2020-07-17 scripts/manuscript.Rmd
fix error in missing submeta

# order the observations by Group, then time, then replicate
orderedMeta<-colData(moanin_model)
ord = order(
  submeta$Group,
  submeta$Timepoint,
  submeta$Replicate)
submeta$Timepoint = as.factor(submeta$Timepoint)

submeta = submeta[ord, ]

res = aheatmap(
    assay(moanin_model[genes_to_plot,ord]),
    Colv=NA,
    color="YlGnBu",
    annCol=submeta[,
                c("Group", "Timepoint")],
    annLegend=FALSE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(raw)"),
    treeheight=0, legend=FALSE)

# Now use the results of the previous call to aheatmap to reorder the genes.
aheatmap(
    rescale_values(moanin_model[genes_to_plot,ord])[res$rowInd,],
    Colv=NA,
    Rowv=NA,
    annCol=submeta[,
                c("Group", "Timepoint")],
    annLegend=TRUE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(rescaled)"),
    treeheight=0)

>>>>

# order the observations by Group, then time, then replicate
orderedMeta<-colData(moanin_model)
ord = order(
  orderedMeta$Group,
  orderedMeta$Timepoint,
  orderedMeta$Replicate)
orderedMeta$Timepoint = as.factor(orderedMeta$Timepoint)

orderedMeta = orderedMeta[ord, ]

res = aheatmap(
    assay(moanin_model[genes_to_plot,ord]),
    Colv=NA,
    color="YlGnBu",
    annCol=orderedMeta[,
                c("Group", "Timepoint")],
    annLegend=FALSE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(raw)"),
    treeheight=0, legend=FALSE)

# Now use the results of the previous call to aheatmap to reorder the genes.
aheatmap(
    rescale_values(moanin_model[genes_to_plot,ord])[res$rowInd,],
    Colv=NA,
    Rowv=NA,
    annCol=orderedMeta[,
                c("Group", "Timepoint")],
    annLegend=TRUE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(rescaled)"),
    treeheight=0)
